---
title: "Food consumption and CO2 emissions due to food products (tidytuesday contribution)"
author: "Rubén F. Bustillo"
date: 2020-02-21
categories: ["R"]
tags: ["tidytuesday", "food consumption"]
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(collapse = TRUE)

```


**Re**

In this post, intented to be a small contribution to the tidytuesday project, we will use the package {echarts4r} to visualizate in a map the food consumption and CO2 emissions from 130 countries.

\

# Intro

\

This short post is going to be my first and small contribution to [Tidytuesday project](https://github.com/rfordatascience/tidytuesday). I will use the package {echarts4r} to plot in a map the food consumption and CO2 emissions due to food products. To some extent the procedure is practically identical to the one used in this [previous post](https://rquer.netlify.com/maps3d/) where it is exposed in a slightly more extensive way how to make the maps using {echarts4r}.

\

## libraries

```{r, warning=FALSE, message=FALSE}

library(tidyverse)
library(echarts4r)

```

\

## dataset

```{r, message=FALSE}

food_consumption <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-18/food_consumption.csv')

```

\

A few modifications:

\

```{r}

map <- food_consumption %>% 
  group_by(country) %>%
  summarise(co2_total = sum(co2_emmission),
            consumption_total = sum(consumption)) %>%
  mutate(country = recode_factor (country,
                                  `USA` = "United States",
                                  `Czech Republic`= "Czech Rep.",
                                  `South Korea`= "Korea"))

```

\

## Choropleth Map: Total CO2 emissions due to food products

```{r, out.width= "100%"}

map %>%
  e_charts(country) %>%
  e_map(co2_total) %>%
  e_visual_map(min=0, max=2000) %>%
  e_title("Total CO2 emissions due to food products \n (kg CO2/person/year)", left = "center") %>%
  e_theme("vintage")

```

\

## 3D map: Total CO2 emissions due to food products

```{r, out.width= "100%"}
map %>%
  e_charts(country) %>%
  e_map_3d(co2_total) %>%
  e_visual_map(min=0, max=2000) %>%
  e_title("Total CO2 emissions due to food products \n (kg CO2/person/year)", left = "center") %>%
  e_theme("vintage")

```

\

## Choropleth Map: Total food consumption

```{r, out.width= "100%"}

map %>%
  e_charts(country) %>%
  e_map(consumption_total) %>%
  e_visual_map(min=0, max=700) %>%
  e_title("Total food consumption \n (kg/person/year)", left = "center") %>%
  e_theme("vintage")

```

\

## 3D map: Total food consumption

```{r, out.width= "100%"}

map %>%
  e_charts(country) %>%
  e_map_3d(consumption_total) %>%
  e_visual_map(min=0, max=700) %>%
  e_title("Total food consumption \n (kg/person/year)", left = "center") %>%
  e_theme("vintage")

```


