---
title: 'Data visualization: Interactive and animated maps with {ggplot2} and {plotly}'
author: "Rubén F. Bustillo"
date: '2020-03-28'
tags: ["maps"]
categories: ["R"]
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(collapse = TRUE)

```

**Re**

In this post we will present a few examples of interactive and animated maps using both {ggplot2} and {plotly} .  
This post is a continuation of the previous one ( interactive and animated maps ) . 

\

# Libraries / packages

\

This post is just a continuation of the [previous post](https://rquer.netlify.com/interactive_map/) on animated and interactive maps. We will show four examples of maps created using {ggplot2} and {plotly}. 

\

```{r, warning=FALSE, message=FALSE}

library(tidyverse)
library(gapminder)
library(echarts4r)
library(gganimate)
library(ggiraph)
library(widgetframe)
library(ggthemes)
library(plotly)
library(viridis)
library(DT)
```

\

# Datasets

\

## gapminder dataset:

\

```{r}

world <- map_data("world") %>%
  filter(region != "Antarctica")

```


```{r, warning=FALSE, message=FALSE}

gapminder_codes <- gapminder::country_codes

gapminder <-gapminder::gapminder_unfiltered


gapminder <- gapminder %>%
  inner_join(gapminder_codes, by= "country") %>%
  mutate(code = iso_alpha)

gapminder_data <- gapminder %>%
  inner_join(maps::iso3166 %>%
               select(a3, mapname), by= c(code = "a3")) %>%
  mutate(mapname = str_remove(mapname, "\\(.*"))


```

\

## Meteorites dataset

\

```{r, warning=FALSE, message=FALSE}

meteoritos <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-11/meteorites.csv")

options(scipen = 999) 

meteoritos_Mundo <- meteoritos %>%
  filter(fall == "Fell") %>%
  filter(year > 1800) %>%
  drop_na() %>%
  arrange(mass)


```

\


# Example 1.

\

```{r, out.width="100%", warning=FALSE}

mapa_animado_1 <- world %>%
  ggplot() +
  geom_polygon(aes( x= long, y = lat, group = group),
               fill = "grey20",
               color = "white",
               size = 0.01) +
  geom_point(data= meteoritos_Mundo, 
             aes(x = long, 
                 y = lat, 
                 size = mass),
             color = "orange",
             alpha = 0.7) +
  labs( title = "Meteorite Landings \n from 1800 to 2013}",
        caption = "The Meteoritical Society") +
  theme_map() +
  scale_size_continuous(guide = F) +
  scale_color_discrete(name = "Type") +
  theme(plot.title = element_text(size = 10, hjust = 0.5))


fig_1 <- ggplotly(mapa_animado_1)

fig_1

```

\

# Example 2.

\


```{r, out.width="100%", warning=FALSE}

mapa_animado_2 <- world %>%
  ggplot() +
  geom_polygon(aes( x= long, y = lat, group = group),
               fill = "grey20",
               color = "white",
               size = 0.01) +
  geom_point(data= meteoritos_Mundo, 
             aes(x = long, 
                 y = lat, 
                 frame = year,
                 size = mass),
             color = "orange",
             alpha = 0.7) +
  labs( title = "Meteorite Landings \n from 1800 to 2013}",
        caption = "The Meteoritical Society") +
  theme_map() +
  scale_size_continuous(guide = F) +
  scale_color_discrete(name = "Type") +
  theme(plot.title = element_text(size = 10, hjust = 0.5))


fig_2 <- ggplotly(mapa_animado_2)%>%
  animation_slider(currentvalue = list(prefix = "Year ", font = list(color="orange")))

fig_2

```

\

# Example 3

\

```{r, out.width="100%", warning=FALSE}

mapa_animado_3 <- gapminder_data %>%
 filter(year == 2007) %>%
  right_join(world, by= c(mapname = "region")) %>%
  ggplot(aes(long, lat, 
             group= group, 
             fill= lifeExp)) +
  geom_polygon(color = "white", 
               size = 0.01) +
  theme_void() +
  scale_fill_viridis(option = "B",
                     name= "Years",
                     guide = guide_colorbar(
                       direction = "horizontal",
                       barheight = unit(2, units = "mm"),
                       barwidth = unit(100, units = "mm"),
                       draw.ulim = FALSE,
                       title.position = "top",
                       title.hjust = 0.5,
                       title.vjust = 0.5 )) +
  labs(title="Life Expectancy",
       subtitle = "year: 2007",
       caption = "Source: gapminder.org")  +
  theme(
    plot.title = element_text(size = 12, hjust = 0.5),
    plot.subtitle = element_text(size = 10, hjust = 0.5),
    plot.caption = element_text(size = 8, hjust = 1),
    legend.position = "bottom") +
  coord_fixed(ratio = 1.3) 



fig_3 <- ggplotly(mapa_animado_3)

fig_3

```

\

# Example 4. 

\

```{r, out.width="100%", warning=FALSE}

mapa_animado_4 <- gapminder_data %>%
 filter(year %in% c(1992, 1997, 2002, 2007)) %>%
  right_join(world, by= c(mapname = "region")) %>%
  ggplot(aes(long, lat, 
             group= group, 
             fill= lifeExp)) +
  geom_polygon(aes(frame = year),
               color = "white", 
               size = 0.01) +
  theme_void() +
  scale_fill_viridis(option = "B",
                     name= "Years",
                     guide = guide_colorbar(
                       direction = "horizontal",
                       barheight = unit(2, units = "mm"),
                       barwidth = unit(100, units = "mm"),
                       draw.ulim = FALSE,
                       title.position = "top",
                       title.hjust = 0.5,
                       title.vjust = 0.5 )) +
  labs(title="Life Expectancy",
       subtitle = "",
       caption = "Source: gapminder.org")  +
  theme(
    plot.title = element_text(size = 12, hjust = 0.5),
    plot.subtitle = element_text(size = 10, hjust = 0.5),
    plot.caption = element_text(size = 8, hjust = 1),
    legend.position = "bottom") +
  coord_fixed(ratio = 1.3) 



fig_4 <- ggplotly(mapa_animado_4) %>%
  animation_slider(currentvalue = list(prefix = "Year ", font = list(color="orange")))

fig_4

```