---
title: "Data visualization: Treemaps with {treemap}, {d3treeR} and {highcharter}"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    orientation: columns
    source_code: embed
    vertical_layout: fill
    theme: paper
---



```{r setup, include=FALSE}


# PACKAGES / LIBRARIES:

library(flexdashboard)
library(tidyverse)
library(plotly)
library(leaflet)
library(rnaturalearth)
library(treemap)
library(d3treeR)
library(highcharter)
library(readxl)
library(stringr)
library(knitr)
library(DT)
library(viridisLite)

options(scipen=10000)

```

Peru
===========================================================================

Column {data-width=300}
---------------------------------------------------------------------------

### 

\

This dashboard is a continuation of a [previous post](https://rquer.netlify.com/sunburst_treemaps#peru). As we explained in there, in a **treemap chart** each brand of a "tree" is given a rectangle, which is then tiled with smaller rectangles. Then, each area is proportional to a specified dimension of the data. **Treemaps** are very useful for displaying hierarchical data. In the post mentioned we explained how to create interactive sunburst charts and treemaps using {plotly}. In this occasion we will show how to create static treemaps using {treemap} and animated treemaps with {d3treeR} and {highcharter}. The treemaps created with {highcharter} are, in my opinion, especially beautiful and very functional. However, note that although {highcharter} is free for personal users, schools, ngos, etc., it is not free for commercial or governmental use. 


On the other hand, the map of Peru is created using {leaflet}. The tootips have been customized to show the name of each region when the user hovers over a region. When clicking on one region it will show the total GVA of the region selected and the % with respect to the total GVA of the country. The provider of the base map is `Esri.WorldShadedRelief`. 


The dashboard presents the data in DaTables using {DT}. It is also possible to customize DataTables, as we will show in the examples. DataTables provides filtering, sorting, pagination and other features. 


We will use again data related to the **regional and sectoral productive structure of Peru for 2018**. Data comes from the Peruvian National Institute of Statistics and Informatics ([INEI](https://www.inei.gob.pe/)). 


The INEI distinguishes 12 major economic / productive sectors: 

- Agriculture, Livestock, Hunting and Forestry.
- Fishing and Aquaculture.
- Extraction of Minerals, Gas and Oil.
- Manufacturing.
- Electricity, Gas and Water.
- Construction.
- Commerce.
- Transportation, Storage, Mail and Messaging.
- Accommodation and Restaurants.
- Telecommunications and Other Information Services.
- Public Administration and Defence.
- Other Services.

\






Column
---------------------------------------------------------------------------

### Gross Value Added by region (in constant 2007 PEN thousands) and % of total GVA, 2018

```{r}

library(readxl)
peru_mapa_vab2018 <- read_excel("C:/Users/Usuario/Desktop/r_que_r/r_que_r/content/datasets/peru_mapa_vab2018.xlsx")

peru_mapa_vab2018$Vab_perc <- formatC(peru_mapa_vab2018$Vab_perc, digits=3)
peru_mapa_vab2018$Vab_perc <- as.numeric(peru_mapa_vab2018$Vab_perc)
peru_mapa_vab2018$vab_2018<- format(peru_mapa_vab2018$vab_2018, big.mark = ",")


peru_map_region <- rnaturalearth::ne_states(country = "Peru", returnclass = "sf") %>%
  select(name, iso_3166_2, geometry) %>%
 left_join(peru_mapa_vab2018, 
            by = "name") 


peru_map_region %>%
  leaflet() %>%
  addProviderTiles(providers$Esri.WorldShadedRelief) %>%
  addPolygons(
    weight = 1,
    label = ~ name,
    color = "darkgreen",
    popup = ~paste("Region:", name,
                   "<br/>",
                   "GVA:", vab_2018,
                   "<br/>",
                   "% GVA:", Vab_perc))

```



Column 
---------------------------------------------------------------------------

### Productive Economic Structure by region, 2018. (GVA in constant 2007 PEN thousands)

```{r}


Peru_vab_sectores <- read_excel("C:/Users/Usuario/Desktop/r_que_r/r_que_r/content/datasets/Peru_vab_sectores_2.xlsx")


names(Peru_vab_sectores) = c("Regions", "AGR", "PES", "EXT", "MAN", "ELEC", "CONS", "COM", "TRANS", "REST", "TELEC", "ADPUB", "OS")


x<-Peru_vab_sectores %>%
  group_by(Regions) %>%
  mutate(total= AGR + PES + EXT + MAN + ELEC + CONS + COM + TRANS + REST + TELEC + ADPUB + OS) %>%
  arrange(total) %>%
  ungroup()

x$Regions = factor(x$Regions, levels = x$Regions)

plotly::plot_ly(data = x,
                y = ~ Regions,
                x = ~ AGR, 
                orientation = 'h',
                name = 'Agriculture, Livestock, Hunting and Forestry', 
                type = 'bar') %>%
  plotly::add_trace( x = ~ PES, 
                     name = "Fishing and Aquaculture") %>% 
  plotly::add_trace( x = ~ EXT, 
                     name = "Extraction of Minerals, Gas and Oil") %>% 
  plotly::add_trace( x = ~ MAN, 
                     name = "Manufacturing") %>%
  plotly::add_trace( x = ~ ELEC, 
                     name = "Electricity, Gas and Water") %>%
  plotly::add_trace( x = ~ CONS, 
                     name = "Construction") %>% 
  plotly::add_trace( x = ~ COM, 
                     name = "Commerce") %>% 
  plotly::add_trace( x = ~ TRANS, 
                     name = "Transportation, Storage, Mail and Messaging") %>%
  plotly::add_trace( x = ~ REST, 
                     name = "Accommodation and Restaurants") %>%
  plotly::add_trace( x = ~ TELEC, 
                     name = "Telecommunications and Other Information Services") %>%
  plotly::add_trace( x = ~ ADPUB, 
                     name = "Public Administration and Defence") %>%
  plotly::add_trace( x = ~ OS, 
                     name = "Other Services") %>%
  plotly::layout(title = " Gross Value Added by region and sector \n (constant 2007 PEN thousands)",
                 barmode = 'stack', 
                 legend = list(x = 0.5, y = 0.1),
                 yaxis = list(title = ""),
                 xaxis = list(title = "Source: INEI | Lima includes Callao en Lima Province"),
                 hovermode = "compare",
                 margin = list(
                   l = 20,
                   r = 10,
                   b = 10,
                   t = 80,
                   pad = 2
                 ))




```





datatable- DT
====================================================================================

Columna {data-width=700}
---------------------------------------------------------------------------

\

### Datatable with fixed column, `info = T`, `sort = T`, and values centered. 

\

```{r}


Peru_vab_sectores <- read_excel("C:/Users/Usuario/Desktop/r_que_r/r_que_r/content/datasets/Peru_vab_sectores_2.xlsx")


datatable(Peru_vab_sectores, 
          rownames = F,
          extensions = "FixedColumns",
          options = list(
            info = TRUE, 
            sort = TRUE,
            fixedColumns = list(leftColumns = 1),
            columnDefs = list(list(className = 'dt-center', targets = 1:12))
          )
          ) 


```

\



Columna {data-width=300}
---------------------------------------------------------------------------

\

### Datatable with `filter= bottom`, `class= 'cell-border stripe'`, `searching= T`

\

```{r}

Peru_sectores <- Peru_vab_sectores %>%
  gather(key = "sector", value = "vab", 2:13)


datatable(Peru_sectores, 
          filter = "bottom",
          rownames = FALSE,
          class = 'cell-border stripe',
          extensions = "FixedColumns",
          options = list(
            searching = TRUE,
            info = TRUE, 
            sort = TRUE,
            fixedColumns = list(leftColumns = 1))
          )


```


Few questions about the data
=================================================================================

Column
------------------------------------------------------------------------------

### **1. REGIONAL CONTRIBUTION TO NATIONAL GVA (DESC)**

```{r}

a <- Peru_sectores %>%
  group_by(Regions) %>%
  summarise(vab_regional = sum(vab)) %>%
  mutate(total= sum(vab_regional), percent = 100*(vab_regional/total)) %>%
  arrange(desc(percent)) %>%
  select(Regions, percent) %>%
  ungroup()

a$percent <- formatC(a$percent, format = "f", digits = 2)

datatable(a)

```


### **2. SECTORAL CONTRIBUTION TO NATIONAL GVA (DESC)**

```{r}

b <- Peru_sectores %>%
  group_by(sector) %>%
  summarise(vab_regional = sum(vab)) %>%
  mutate(total= sum(vab_regional), percent = 100*(vab_regional/total)) %>%
  arrange(desc(percent)) %>%
  select(sector, percent) %>%
  ungroup()

b$percent <- formatC(b$percent, format = "f", digits = 2)

datatable(b)

```

Column
------------------------------------------------------------------------------

### **3. SECTORAL CONTRIBUTION OF EACH REGION TO NATIONAL GVA (DESC)**

```{r}

c <- Peru_sectores %>%
  mutate(suma_total= sum(vab), percent= 100*(vab/suma_total)) %>%
  select(Regions, sector,percent) %>%
  arrange(desc(percent)) 

c$percent <- formatC(c$percent, format = "f", digits = 2)
  
datatable(c)
```

### **4. SECTORAL CONTRIBUTION TO REGIONAL GVA (DESC by region)** 

```{r}

d <- Peru_sectores %>%
  group_by(Regions) %>%
  mutate(suma_total= sum(vab), percent= 100*(vab/suma_total)) %>%
  select(Regions, sector, percent) %>%
  arrange(Regions, desc(percent)) %>%
  ungroup()

d$percent <- formatC(d$percent, format = "f", digits = 2)

datatable(d)

```

Column
------------------------------------------------------------------------------

### **5. REGIONAL CONTRIBUTION TO SECTORAL GVA (DESC by sector)**

```{r}

e <- Peru_sectores %>%
  group_by(sector) %>%
  mutate(suma_total= sum(vab), percent= 100*(vab/suma_total)) %>%
  select(sector, Regions, percent) %>%
  arrange(sector, desc(percent)) %>%
  ungroup()

e$percent <- formatC(e$percent, format = "f", digits = 2)

datatable(e)

```

### **6. SECTOR IN EACH REGION THAT CONTRIBUTES MOST TO NATIONAL GVA (DESC by %)**

```{r}

f <- Peru_sectores %>%
  mutate(suma_total= sum(vab), percent= 100*(vab/suma_total)) %>%
  select(Regions, sector, percent) %>%
  arrange(desc(percent)) %>%
  group_by(Regions) %>%
  top_n(1) %>%
  ungroup()

f$percent <- formatC(f$percent, format = "f", digits = 2)

datatable(f)

```



{treemap}
====================================================================================


### Example I. Sectoral Level


```{r, fig.width=14, fig.height=8}

tree_sectores <- treemap(
  Peru_sectores,
  index=c("sector","Regions"),
  vSize="vab",
  title = "GVA, economic sector and region, 2018 ",
  vColor="sector",
  type="index",
  force.print.labels = F,
  border.col = c("black", "white"),
  border.lwds = c(3,2),
  align.labels = list(
    c("center","center"),
    c("center", "top")
  )
)



```


{treemap} II
====================================================================================


### Example II. Regional Level


```{r, fig.width=14, fig.height=8}

tree_regions <- treemap(
  Peru_sectores,
  index=c("Regions", "sector"),
  vSize="vab",
  title = "GVA, region and economic sector, 2018 ",
  vColor="vab",
  type="value",
  palette = "BuPu",
  force.print.labels = F,
  border.col = c("black", "white"),
  border.lwds = c(3,2),
  align.labels = list(
    c("center","center"),
    c("center", "top")
  )
)

```


{d3treeR} 
====================================================================================

### Example I. Sectoral Level

```{r}

d3tree(tree_sectores,
       rootname = "GVA, economic sector and region, 2018")

```



{d3treeR} II
====================================================================================


### Example II. Regional Level

```{r}

d3tree(tree_regions,
       rootname = "GVA, region and economic sector, 2018")

```



 {highcharter}
====================================================================================

### Example I. Sectoral Level

```{r}

hctreemap(tree_sectores, allowDrillToNode = TRUE) %>%
  hc_title(text = "GVA, economic sector and region, 2018") %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
                            GVA: {point.value:,.0f}") %>%
  hc_exporting(enabled = TRUE)

```



{highcharter} II
====================================================================================

### Example II. Regional Level

```{r}

hctreemap(tree_regions, allowDrillToNode = TRUE) %>%
  hc_title(text = "GVA, region and economic sector, 2018") %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
                            GVA: {point.value:,.0f}") %>%
  hc_exporting(enabled = TRUE)

```