---
title: "Data Visualizations: Bar Charts"
author: "Rubén F. Bustillo"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    source_code: embed
    vertical_layout: fill
    theme: journal
---

```{r setup, include=FALSE}

# PACKAGES / LIBRARIES:

library(flexdashboard)
library(tidyverse)
library(gapminder)
library(ggthemes)
library(ggthemr)



# DATASET:

gapminder <- gapminder::gapminder


```

Sheet A
====================================================================================


Column 
-----------------------------------------------------------------------

### `summarise(promedio = mean(lifeExp))`

```{r}

# DATASET: AVERAGE LIFE EXPECTANCY BY CONTINENT IN 2007

grafico_edad_promedio <- gapminder %>%
  filter(year == 2007) %>%
  group_by(continent) %>%
  summarise(promedio = mean(lifeExp))



# GGTHEMR THEME: FLAT (More themes: https://rquer.netlify.com/ggplot_themes#themes-a)

ggthemr("flat")


# BASIC PLOT:

ggplot(grafico_edad_promedio, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy")


```

###  `reorder(continent, -promedio, sum)`

```{r}

# PLOT: ORDERED BY AVERAGE LIFE EXPECTANCY (DESCENDENT)

ggplot(grafico_edad_promedio, 
       aes(x= reorder(continent, -promedio, sum), 
           y= promedio, fill=continent)) + 
  geom_col() + 
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy", 
       fill = NULL) 

```



Column 
-----------------------------------------------------------------------

### `x= reorder(continent, promedio, sum)`

```{r}

# PLOT: ORDERED BY AVERAGE LIFE EXPECTANCY (ASCENDENT). 
# LEGEND HAS BEEN REMOVED

ggplot(grafico_edad_promedio, 
       aes(x= reorder(continent, promedio, sum), 
           y= promedio, fill=continent)) + 
  geom_col() + 
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy", 
       fill = NULL) +
  guides(fill = FALSE)

```


### `scale_x_date(breaks = grafico_spain$year, date_labels = "%Y")` / `geom_col(fill = "limegreen", alpha = 0.8)`


```{r}

# CONVERT YEAR COLUMN TO DATE FORMAT:

grafico_spain <- filter(gapminder, 
             country == "Spain") %>% 
  mutate(year = as.Date(paste(year, 
                              "-01-01", 
                              sep = "", 
                              format = "%Y-%b-%d")))


# PLOT: EVOLUTION OF LIFE EXPECTANCY BY YEAR. 

ggplot(grafico_spain, aes(x = year, 
               y = lifeExp)) + 
  geom_col(fill = "limegreen",     
           alpha = 0.8) + 
  scale_x_date(breaks = grafico_spain$year, 
               date_labels = "%Y") + 
  scale_y_continuous(expand = c(0, 0)) + #
  labs(title = "Life expectancy in Spain", 
       subtitle = "Period: 1952-2007", 
       x = NULL, 
       y = "life expectancy") 

```



Column 
-----------------------------------------------------------------------

### `coord_flip()`

```{r}

# PLOT: COORD_FLIP

ggplot(grafico_edad_promedio, 
       aes(x= reorder(continent, promedio, sum), 
           y= promedio, fill=continent)) + 
  geom_col() + 
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy", 
       fill = NULL) +
  coord_flip()

```

### `coord_flip()`

```{r}

# PLOT: COORD_FLIP

ggplot(grafico_edad_promedio, 
       aes(x= reorder(continent, -promedio, sum), 
           y= promedio, fill=continent)) + 
  geom_col() + 
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy", 
       fill = NULL) +
  coord_flip()

```



Sheet B
=============================================================

column
----------------------------------------------------------

### Cambio de tamaño, color y estilo del texto de los ejes y título. 

```{r}

# LETTER FONTS:

library(extrafont)
loadfonts(device = "win")


# DATA: TOTAL POPULATION BY CONTINENT AND YEAR

poblacion_total <- gapminder %>% 
  group_by(year, continent) %>% 
  summarise(poblacion = sum(as.double(pop)))


# PLOT: WE HAVE CHANGED THE TITLE AND SUBTITLE (COLOR, FONT, SIZE ..), AND AXIS TEXT.

ggplot(poblacion_total, 
       aes(x = year, 
           y = poblacion, 
           fill = continent)) + 
  geom_col(colour = "white",
           size = 0.2) + 
  scale_x_continuous(breaks = seq(1952, 2007, 5), 
                     expand = c(0, 0)) + 
  scale_y_continuous(labels = scales::comma, 
                     expand = c(0, 0)) + 
  labs(title = "Total population by continent", 
       subtitle = "From 1952 to 2007", 
       x = NULL, 
       y = NULL) +
  theme (axis.text.x = element_text(face="italic", colour="red", size=rel(0.8)),
         axis.text.y = element_text(face="italic", colour="red", size=rel(0.8))) +
  theme (plot.title = element_text(family = "Comic Sans MS",
                                   size = rel(2),
                                   hjust = 0.5,
                                   face = "bold",
                                   color = "orange",
                                   lineheight = 1.2)) +
  theme (plot.subtitle = element_text(family = "Comic Sans MS",
                                   size = rel(1.2),
                                   hjust = 0.5,
                                   face = "bold",
                                   color = "orange",
                                   lineheight = 1.2)) 
  

```



### `guides(fill = guide_legend(reverse = T))`

```{r}

# DATA: ONLY FOR YEAR >= 1977

poblacion_total_b <- gapminder %>% 
  group_by(year, continent) %>% 
  filter(year >= 1977) %>%
  summarise(poblacion = sum(as.double(pop)))


# PLOT: THE ORDER OF THE LEGEND HAS BEEN CHANGED

ggplot(poblacion_total_b, 
       aes(x = year, 
           y = poblacion, 
           fill = continent)) + 
  geom_col(colour = "white",
           size = 0.2) + 
  scale_x_continuous(breaks = seq(1977, 2007, 5), 
                     expand = c(0, 0)) + 
  scale_y_continuous(labels = scales::comma, 
                     expand = c(0, 0)) + 
  guides(fill = guide_legend(reverse = T)) + 
  labs(title = "Total population by continent", 
       subtitle = "From 1977 to 2007", 
       x = NULL, 
       y = NULL) 

```


column
----------------------------------------------------------

### `geom_col(position = "fill)`

```{r}

# PLOT: POSITION = FILL

ggplot(poblacion_total, 
       aes(x = year, 
           y = poblacion, 
           fill = continent)) + 
  geom_col(position = "fill", 
           colour = "white",
           size = 0.2) + 
  scale_x_continuous(breaks = seq(1952, 2007, 5), 
                     expand = c(0, 0)) + 
  scale_y_continuous(labels = scales::percent, 
                     expand = c(0, 0)) + 
  labs(title = "Total population by continent", 
       subtitle = "From 1952 to 2007", 
       x = NULL, y = NULL)


```

### `theme (axis.text.x = element_text(face = "bold", colour = "red", size = rel(1.2), angle = 45, hjust = 1))`

```{r}

# PLOT: 

ggplot(poblacion_total_b, 
       aes(x = year, 
           y = poblacion, 
           fill = continent)) + 
  geom_col(position = "fill", 
           colour = "white",
           size = 0.2) + 
  scale_x_continuous(breaks = seq(1977, 2007, 5), 
                     expand = c(0, 0)) + 
  scale_y_continuous(labels = scales::percent, 
                     expand = c(0, 0)) + 
  labs(title = "Total population by continent", 
       subtitle = "From 1977 to 2007", 
       x = NULL, y = NULL) +
  theme (axis.text.x = element_text(face = "bold", 
                                    colour = "red",
                                    size = rel(1.2),
                                    angle = 45,
                                    hjust = 1)) 

```


column
----------------------------------------------------------

### `geom_col(position = "dodge)`

```{r}

# PLOT: POSITION = DODGE

ggplot(poblacion_total, 
       aes(x = year, 
           y = poblacion, 
           fill = continent)) + 
  geom_col(position = "dodge", 
           colour = "white",
           size = 0.2) + 
  scale_x_continuous(breaks = seq(1952, 2007, 5), 
                     expand = c(0, 0)) + 
  scale_y_continuous(labels = scales::comma, 
                     expand = c(0, 0)) + 
  labs(title = "Total population by continent and year", 
       subtitle = "From 1952 to 2007", 
       x = NULL, y = NULL)


```


### `scale_fill_discrete(guide = guide_legend(title = "Año", keywidth = 2, keyheight = 2))
`

```{r}

poblacion_total_c <- gapminder %>% 
  group_by(year, continent) %>% 
  filter(year >= 1992) %>%
  summarise(poblacion = sum(as.double(pop)))


ggplot(poblacion_total_c, 
       aes(x = continent, 
           y = poblacion, 
           fill = factor(year))) + 
  geom_col(position = "dodge", 
           colour = "white",
           size = 0.2) + 
  #scale_x_continuous(expand = c(0, 0)) + 
  scale_y_continuous(labels = scales::comma, 
                     expand = c(0, 0)) + 
  labs(title = "Total population by continent and year", 
       subtitle = "From 1992 to 2007", 
       x = NULL, y = NULL) +
  scale_fill_discrete(guide = guide_legend(title = "Año", 
                                             keywidth = 2, 
                                             keyheight = 2))

```




Sheet C
=============================================================

column
----------------------------------------------------------

### `scale_x_discrete(limit = c("Africa"))` 

```{r}

# PLOT: LIMIT AFRICA

ggplot(poblacion_total_b, 
       aes(x = continent, 
           y = poblacion, 
           fill = factor(year))) + 
  geom_col(position = "dodge", 
           colour = "white",
           size = 0.2) + 
  #scale_x_continuous(expand = c(0, 0)) + 
  scale_y_continuous(labels = scales::comma, 
                     expand = c(0, 0)) + 
  labs(title = "Total population by year in Africa", 
       subtitle = "From 1977 to 2007", 
       x = NULL, y = NULL) +
  scale_fill_discrete(guide = guide_legend(title = "Año")) +
  scale_x_discrete(limit = c("Africa"))

```


### `scale_x_discrete(limit = c("Africa", "Europe"))`

```{r}

# PLOT: LIMIT AFRICA AND EUROPE

ggplot(poblacion_total_b, 
       aes(x = continent, 
           y = poblacion, 
           fill = factor(year))) + 
  geom_col(position = "dodge", 
           colour = "white",
           size = 0.2) + 
  #scale_x_continuous(expand = c(0, 0)) + 
  scale_y_continuous(labels = scales::comma, 
                     expand = c(0, 0)) + 
  labs(title = "Total population by year in Africa & Europe", 
       subtitle = "From 1977 to 2007", 
       x = NULL, y = NULL) +
  scale_fill_discrete(guide = guide_legend(title = "Año")) +
  scale_x_discrete(limit = c("Africa", "Europe"))

```

column
----------------------------------------------------------

### `scale_x_discrete(limit = c("Europe", "Africa"))`

```{r}

# PLOT: LIMIT TO EUROPE AND AFRICA (ORDER CHANGED)

ggplot(poblacion_total_b, 
       aes(x = continent, 
           y = poblacion, 
           fill = factor(year))) + 
  geom_col(position = "dodge", 
           colour = "white",
           size = 0.2) + 
  #scale_x_continuous(expand = c(0, 0)) + 
  scale_y_continuous(labels = scales::comma, 
                     expand = c(0, 0)) + 
  labs(title = "Total population by year in Europe & Africa", 
       subtitle = "From 1977 to 2007", 
       x = NULL, y = NULL) +
  scale_fill_discrete(guide = guide_legend(title = "Año")) +
  scale_x_discrete(limit = c("Europe", "Africa"))

```


### `scale_y_continous(limit = c(0, 1000000000))`

```{r}

# PLOT: SIZE OF Y AXIS REDUCED TO 0-1000 MILLION

ggplot(poblacion_total_b, 
       aes(x = continent, 
           y = poblacion, 
           fill = factor(year))) + 
  geom_col(position = "dodge", 
           colour = "white",
           size = 0.2) + 
  #scale_x_continuous(expand = c(0, 0)) + 
  scale_y_continuous(labels = scales::comma, 
                     expand = c(0, 0),
                     limit = c(0, 1000000000)) + 
  labs(title = "Total population by year in Africa & Europe", 
       subtitle = "From 1977 to 2007", 
       x = NULL, y = NULL) +
  scale_fill_discrete(guide = guide_legend(title = "Año")) +
  scale_x_discrete(limit = c("Africa", "Europe"))

```


column
----------------------------------------------------------

### `scale_x_discrete(labels = c("AFR", "AME", "ASI", "EUR", "OCE"))`

```{r}

# PLOT: X LABELS MODIFIED. 

ggplot(grafico_edad_promedio, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy") +
  scale_x_discrete(labels = c("AFR", "AME", "ASI", "EUR", "OCE"))

```


### `scale_x_discrete(breaks = c("Asia"))`

```{r}

# PLOT: SOME LABELS (X AXIS) HAVE BEEN REMOVED

ggplot(poblacion_total_b, 
       aes(x = continent, 
           y = poblacion, 
           fill = factor(year))) + 
  geom_col(position = "dodge", 
           colour = "white",
           size = 0.2) + 
  #scale_x_continuous(expand = c(0, 0)) + 
  scale_y_continuous(labels = scales::comma, 
                     expand = c(0, 0)) + 
  labs(title = "Total population by year in Asia \n Compared to the other continents", 
       subtitle = "From 1992 to 2007", 
       x = NULL, y = NULL) +
  scale_fill_discrete(guide = guide_legend(title = "Año")) +
  scale_x_discrete(breaks = c("Asia"))
```




Sheet D
=============================================================

column
----------------------------------------------------------

### `scale_y_continuous( breaks = seq(0, 80, 10))` 

```{r}

# PLOT: 

ggplot(grafico_edad_promedio, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy") +
  scale_y_continuous( breaks = seq(0, 80, 10))

```

### `scale_x_discrete(breaks = seq(50, 80, 5))`

```{r}

ggplot(grafico_edad_promedio, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy") +
  scale_y_continuous( breaks = seq(50, 80, 5))

```

column
----------------------------------------------------------

### `scale_y_continuous( breaks = c(0, 40, 80))`

```{r}

# PLOT: 

ggplot(grafico_edad_promedio, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy") +
  scale_y_continuous( breaks = c(0, 40, 80))


```


### `scale_y_continuous( breaks = c(54.8, 70.72, 73.60, 77.64, 80.71), labels = c("Africa (54.8)", "Asia (70.7)", "Americas (73.6)", "Europe (77.6)", "Oceania (80.7)"))`

```{r}

# PLOT:

ggplot(grafico_edad_promedio, 
       aes(x= reorder(continent, promedio, sum), 
           y= promedio, fill=continent)) + 
  geom_col() + 
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = NULL, 
       fill = NULL)  +
  scale_y_continuous( breaks = c(54.8, 70.72, 73.60, 77.64, 80.71),
                      labels = c("Africa (54.8)", "Asia (70.7)", "Americas (73.6)", "Europe (77.6)", "Oceania (80.7)"))

```

column
----------------------------------------------------------

### `scale_y_continuous( breaks = NULL)`

```{r}

# PLOT:

ggplot(grafico_edad_promedio, 
       aes(x= reorder(continent, promedio, sum), 
           y= promedio, fill=continent)) + 
  geom_col() + 
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = NULL, 
       fill = NULL)  +
  scale_y_continuous( breaks = NULL)

```

### `scale_y_continuous( trans = "reverse")`

```{r}

# PLOT: REVERSED

ggplot(grafico_edad_promedio, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy") +
  scale_y_continuous( trans = "reverse")



```


Sheet E
====================================================================================


Column 
-----------------------------------------------------------------------

### 

```{r}

# CHANGED NUMBER FORMAT: (more info: https://rquer.netlify.com/formatear_numeros/)

grafico_edad_promedio$promedio_labels <- formatC(grafico_edad_promedio$promedio, format = "f", digits = 2)

# PLOT: 

ggplot(grafico_edad_promedio, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy") +
  geom_text(aes(label=promedio_labels),
            size = 3,
            vjust = -0.4) 
  



```

### 

```{r}

# PLOT: 

ggplot(grafico_edad_promedio, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy") +
  geom_text(aes(label=promedio_labels),
            size = 3.5,
            vjust = 2,
            color = "white",
            fontface = "bold") 

```


Column 
-----------------------------------------------------------------------

### 

```{r}

# PLOT: ANGLE OF TEXT

ggplot(grafico_edad_promedio, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy") +
  geom_text(aes(label=promedio_labels),
            size = 4,
            vjust = -0.1,
            angle = 45,
            fontface = "bold") 

```

### 

```{r}

# CHANGED NUMBER FORMAT: (more info: https://rquer.netlify.com/formatear_numeros/)

grafico_spain$lifeExp_labels <- formatC(grafico_spain$lifeExp, format = "f", digits = 2)

# PLOT:

ggplot(grafico_spain, aes(x = year, 
               y = lifeExp)) + 
  geom_col(fill = "limegreen",     
           alpha = 0.8) + 
  scale_x_date(breaks = grafico_spain$year, 
               date_labels = "%Y") + 
  scale_y_continuous(expand = c(0, 0)) + 
  labs(title = "Life expectancy in Spain", 
       subtitle = "Period: 1952-2007", 
       x = NULL, 
       y = "life expectancy") +
  geom_text(aes(label=lifeExp_labels),
            size = 3.5,
            hjust = 1.2,
            angle = 90,
            color = "white",
            fontface = "bold") 

```


Column 
-----------------------------------------------------------------------

### 

```{r}

# PLOT: 

ggplot(grafico_edad_promedio, 
       aes(x= reorder(continent, promedio, sum), 
           y= promedio, fill=continent)) + 
  geom_col() + 
  labs(title = "Life expectancy (mean) by continent in 2007", 
       x = NULL, 
       y = "Life Expectancy", 
       fill = NULL) +
  coord_flip() +
  geom_text(aes(label = promedio_labels),
            hjust = 2,
            color = "white",
            fontface = "bold")

```

### 

```{r}

# CHANGED NUMBER FORMAT: (more info: https://rquer.netlify.com/formatear_numeros/)

poblacion_total_c$poblacion_label <- formatC(poblacion_total_c$poblacion, format= "f",digits= 0, big.mark = ".") 

# PLOT:

ggplot(poblacion_total_c, 
       aes(x = year, 
           y = poblacion, 
           fill = continent)) + 
  geom_col(position = "fill", 
           colour = "white",
           size = 0.2) + 
  scale_x_continuous(breaks = seq(1977, 2007, 5), 
                     expand = c(0, 0)) + 
  scale_y_continuous(labels = scales::percent, 
                     expand = c(0, 0)) + 
  labs(title = "Total population by continent", 
       subtitle = "From 1992 to 2007", 
       x = NULL, y = NULL) +
  geom_text(aes(label = poblacion_label), 
            position = position_fill(),
            vjust = 2.5,
            color = "white",
            fontface = "bold",
            size = 3.5)+
  guides(fill = FALSE)

ggthemr_reset()

```



Sheet F
=============================================================

column {data-height=250}
----------------------------------------------------------

### `theme_bw()`

```{r, fig.height= 11, fig.width= 6}

# THERE ARE PLENTY OF THEMES WE CAN USE IN OUR CHARTS (https://rquer.netlify.com/ggplot_themes#themes-a). 
# Here I present 4 themes (one by continent). Thanks to https://www.trafforddatalab.io/graphics_companion/ for the inspiration while creating the plots. 



# PLOT: EUROPE

grafico_edad_promedio_europe <- gapminder %>%
  filter ( year == 2007) %>%
  filter (continent == "Europe") %>%
  mutate (median = median(lifeExp),
          diff = lifeExp - median,
          type = ifelse(lifeExp > median, "Above", "Below")) %>%
  arrange (diff) %>%
  mutate(country = factor(country, levels = country))


ggplot(grafico_edad_promedio_europe, aes(x = country, y = diff, label = country)) +
  geom_col(aes(fill = type), width = 0.5) +
  scale_fill_manual(labels = c("Above median", "Below median"),
                    values = c("Above" = "cornflowerblue", "Below" = "firebrick1")) +
  coord_flip()+
  guides(fill = guide_legend(nrow = 1)) +
  theme_bw() +
  theme(legend.position = "top",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs( title = "Continent: Europe",
        subtitle = "Life Expectancy in relation to continent average \n year: 2007",
        x = NULL,
        y = NULL)


```

column {data-height=250}
----------------------------------------------------------

### `theme_gdocs()`



```{r, fig.height= 11, fig.width= 6}

# PLOT: AMERICAS

grafico_edad_promedio_americas <- gapminder %>%
  filter ( year == 2007) %>%
  filter (continent == "Americas") %>%
  mutate (median = median(lifeExp),
          diff = lifeExp - median,
          type = ifelse(lifeExp > median, "Above", "Below")) %>%
  arrange (diff) %>%
  mutate(country = factor(country, levels = country))


ggplot(grafico_edad_promedio_americas, aes(x = country, y = diff, label = country)) +
  geom_col(aes(fill = type), width = 0.5) +
  scale_fill_manual(labels = c("Above median", "Below median"),
                    values = c("Above" = "gold", "Below" = "darkorchid")) +
  coord_flip()+
  guides(fill = guide_legend(nrow = 1)) +
  theme_gdocs()+
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs( title = "Continent: Americas",
        subtitle = "Life Expectancy in relation to continent average \n year: 2007",
        x = NULL,
        y = NULL)

```

column {data-height=250}
----------------------------------------------------------

### `theme_clean()`

```{r, fig.height= 11, fig.width= 6}

# PLOT: ASIA

grafico_edad_promedio_asia <- gapminder %>%
  filter ( year == 2007) %>%
  filter (continent == "Asia") %>%
  mutate (median = median(lifeExp),
          diff = lifeExp - median,
          type = ifelse(lifeExp > median, "Above", "Below")) %>%
  arrange (diff) %>%
  mutate(country = factor(country, levels = country))


ggplot(grafico_edad_promedio_asia, aes(x = country, y = diff, label = country)) +
  geom_col(aes(fill = type), width = 0.5) +
  scale_fill_manual(labels = c("Above median", "Below median"),
                    values = c("Above" = "orange", "Below" = "grey")) +
  coord_flip()+
  guides(fill = guide_legend(nrow = 1)) +
  theme_clean() +
  theme(legend.position = "top",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs( title = "Continent: Asia",
        subtitle = "Life Expectancy in relation to continent average \n year: 2007",
        x = NULL,
        y = NULL)

```

column {data-height=250}
----------------------------------------------------------

### `theme_hc()`

```{r, fig.height= 11, fig.width= 6}

# PLOT: AFRICA

grafico_edad_promedio_africa <- gapminder %>%
  filter ( year == 2007) %>%
  filter (continent == "Africa") %>%
  mutate (median = median(lifeExp),
          diff = lifeExp - median,
          type = ifelse(lifeExp > median, "Above", "Below")) %>%
  arrange (diff) %>%
  mutate(country = factor(country, levels = country))


ggplot(grafico_edad_promedio_africa, aes(x = country, y = diff, label = country)) +
  geom_col(aes(fill = type), width = 0.5) +
  scale_fill_manual(labels = c("Above median", "Below median"),
                    values = c("Above" = "darkturquoise", "Below" = "deeppink2")) +
  coord_flip() +
  theme_hc()+
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs( title = "Continent: Africa",
        subtitle = "Life Expectancy in relation to continent average \n year: 2007",
        x = NULL,
        y = NULL)



```