---
title: "Data Visualizations: Box plots"
author: "Rubén F. Bustillo"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    source_code: embed
    vertical_layout: fill
    theme: journal
---

```{r setup, include=FALSE}

# PACKAGES / LIBRARIES:

library(flexdashboard)
library(tidyverse)
library(gapminder)
library(ggthemes)
library(ggthemr)



# DATASET:

gapminder <- gapminder::gapminder


```

Sheet A
====================================================================================


Column 
-----------------------------------------------------------------------

### `geom_boxplot()`

```{r}

# DATASET: FDP IN SELECTED COUNTRIES BY CONTINENT IN 2007

grafico_gdppercap <- gapminder %>%
  filter(year == 2007) %>%
  group_by(continent)


# GGTHEMR THEME: FLAT (More themes: https://rquer.netlify.com/ggplot_themes#themes-a)

ggthemr("flat")

ggplot(grafico_gdppercap, aes(x = continent, y = gdpPercap, fill = continent)) +
  geom_boxplot() +
  labs(title = "GDP per capita of selected countries by continent",
       subtitle = "year: 2007",
       x = "",
       y = "GDP per capita") 

```

### `geom_boxplot(color = "blue")`  

```{r}

ggplot(grafico_gdppercap, aes(x = continent, y = gdpPercap, fill = continent)) +
  geom_boxplot(color = "blue") +
  labs(title = "GDP per capita of selected countries by continent",
       subtitle = "year: 2007",
       x = "",
       y = "GDP per capita") 

```



Column 
-----------------------------------------------------------------------

### `scale_fill_brewer(palette = "Set2")`

```{r}

ggplot(grafico_gdppercap, aes(x = continent, y = gdpPercap, fill = continent)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "GDp per capita of selected countries by continent",
       subtitle = "year: 2007",
       x = "",
       y = "GDP per capita") 

```


### `scale_fill_brewer(palette = "BuPu")` | `theme(legend.position="none")`

```{r}

ggplot(grafico_gdppercap, aes(x = continent, y = gdpPercap, fill = continent)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "BuPu") +
  labs(title = "GDP percapita of selected countries by continent",
       subtitle = "year: 2007",
       x = "",
       y = "GDP per capita") +
  theme(legend.position="none")

```



Column 
-----------------------------------------------------------------------

### `geom_boxplot(fill="limegreen", alpha=0.2`

```{r}

ggplot(grafico_gdppercap, aes(x = continent, y = gdpPercap)) +
  geom_boxplot(fill="limegreen", alpha=0.2) +
  labs(title = "GDP percapita of selected countries by continent",
       subtitle = "year: 2007",
       x = "",
       y = "GDP per capita") 

```

### `geom_boxplot(fill="cornflowerblue", color= "darkblue", alpha=0.2, notch = TRUE, notchwidth = 0.5, outlier.color = "firebrick1", outlier.fill = "red", outlier.size = 3)`

```{r}

ggplot(grafico_gdppercap, aes(x = continent, y = gdpPercap)) +
  geom_boxplot(fill="cornflowerblue", 
               color= "darkblue",
               alpha=0.2,
               notch = TRUE,
               notchwidth = 0.5,
               outlier.color = "firebrick1",
               outlier.fill = "red",
               outlier.size = 3) +
  labs(title = "GDP percapita of selected countries by continent",
       subtitle = "year: 2007",
       x = "",
       y = "GDP per capita") 

```



Sheet B
====================================================================================


Column 
-----------------------------------------------------------------------

### `grafico_gdppercap$type=factor(ifelse(grafico_gdppercap$continent=="Europe","A","B"))`

```{r}

grafico_gdppercap$type=factor(ifelse(grafico_gdppercap$continent=="Europe","A","B"))

ggplot(grafico_gdppercap, aes(x = continent, y = gdpPercap, fill = type)) +
  geom_boxplot() +
  labs(title = "GDP per capita of selected countries by continent",
       subtitle = "year: 2007",
       x = "",
       y = "GDP per capita") 

```

### `scale_fill_manual(values = c("cornflowerblue", "firebrick1")) + scale_alpha_manual(values = c(0.6, 0.6))`  

```{r}

ggplot(grafico_gdppercap, aes(x = continent, y = gdpPercap, 
                              fill = type,
                              alpha =  type)) +
  geom_boxplot() +
  labs(title = "GDP per capita of selected countries by continent",
       subtitle = "year: 2007",
       x = "",
       y = "GDP per capita") +
  scale_fill_manual(values = c("cornflowerblue", "firebrick1")) + 
  scale_alpha_manual(values = c(0.6, 0.6)) 

```



Column 
-----------------------------------------------------------------------

### `scale_fill_brewer(palette = "Set2")`

```{r}



```


### `scale_fill_brewer(palette = "BuPu")` | `theme(legend.position="none")`

```{r}



```



Column 
-----------------------------------------------------------------------

### `geom_boxplot(fill="limegreen", alpha=0.2`

```{r}



```

### `geom_boxplot(fill="cornflowerblue", color= "darkblue", alpha=0.2, notch = TRUE, notchwidth = 0.5, outlier.color = "firebrick1", outlier.fill = "red", outlier.size = 3)`

```{r}



```
