---
title: "themes {ggplot2}, {ggthemes}, {ggthemer}"
author: "Rubén F. Bustillo"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: yeti
---


```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(gapminder)
library(ggthemes)
library(ggthemr)


gapminder <- gapminder::gapminder


grafico <- gapminder %>%
  filter(year == 2007) %>%
  group_by(continent) %>%
  summarise(promedio = mean(lifeExp))



```


THEMES (a)
=====================================================================

Column 
-----------------------------------------------------------------------

### Default theme

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: default ")

```

### `theme_bw()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_bw() ") +
  theme_bw()

```




Column 
-----------------------------------------------------------------------


### `theme_classic()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_classic() ") +
  theme_classic()

```

### `theme_dark()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_dark() ") +
  theme_dark()

```


Column 
-----------------------------------------------------------------------


### `theme_light()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_light() ") +
  theme_light()

```

### `theme_linedraw()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_linedraw() ") +
  theme_linedraw()

```


THEMES (b)
==============================================================================

Column 
-----------------------------------------------------------------------

### `theme_minimal()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_minimal() ") +
  theme_minimal()
```

### `theme_void()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_void() ") +
  theme_void()

```




Column 
-----------------------------------------------------------------------


### `theme_base()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_base() ") +
  theme_classic() +
  theme_base()

```

### `theme_calc()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_calc()") +
  theme_calc()

```


Column 
-----------------------------------------------------------------------


### `theme_clean()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_clean()") +
  theme_clean()

```

### `theme_economist()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_economist() ") +
  theme_economist()

```

THEMES (c)
==============================================================================

Column 
-----------------------------------------------------------------------

### `theme_economist_white()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_economist_White() ") +
  theme_economist_white()
```

### `theme_excel()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_excel() ") +
  theme_excel()

```




Column 
-----------------------------------------------------------------------


### `theme_excel_new()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_excel_new() ") +
  theme_excel_new() +
  theme_base()

```

### `theme_calc()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_calc() ") +
  theme_calc()

```


Column 
-----------------------------------------------------------------------


### `theme_few()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_few()") +
  theme_few()

```

### `theme_fivethirtyeight()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_fivethirtyeight() ") +
  theme_fivethirtyeight()

```



THEMES (d)
==============================================================================

Column 
-----------------------------------------------------------------------

### `theme_foundation()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_foundation() ") +
  theme_foundation()
```

### `theme_gdocs()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_gdocs() ") +
  theme_gdocs()

```




Column 
-----------------------------------------------------------------------


### `theme_hc()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_hc() ") +
  theme_hc()

```

### `theme_igray()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_igray() ") +
  theme_igray()

```


Column 
-----------------------------------------------------------------------


### `theme_ligth()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_light()") +
  theme_light()

```

### `theme_linedraw()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_linedraw()") +
  theme_linedraw()

```



THEMES (e)
==============================================================================

Column 
-----------------------------------------------------------------------

### `theme_map()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_linedraw()") +
  theme_map()

```

### `theme_pander()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_pander()") +
  theme_pander()

```




Column 
-----------------------------------------------------------------------


### `theme_par()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_par()") +
  theme_par()

```

### `theme_solarized()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_solarized()") +
  theme_solarized()

```


Column 
-----------------------------------------------------------------------


### `theme_solarized_2()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_solarized_2()") +
  theme_solarized_2()

```

### `theme_solid()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_solid()") +
  theme_solid()

```


THEMES (f)
==============================================================================

Column 
-----------------------------------------------------------------------

### `theme_stata()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_stata()") +
  theme_stata()

```

### `theme_wsj()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_wsj()") +
  theme_wsj()

```




Column 
-----------------------------------------------------------------------


### `theme_tufte()`

```{r}

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_tufte()") +
  theme_tufte()

```

### `ggthemr("dust")`

```{r}

ggthemr("dust")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`dust`)")

ggthemr_reset()

```


Column 
-----------------------------------------------------------------------


### `ggthemr("flat")`

```{r}

library(ggthemr)
ggthemr("flat")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`flat`)")

ggthemr_reset()

```

### `ggthemr("camoflauge")`

```{r}

library(ggthemr)
ggthemr("camoflauge")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`camoflauge`)")

ggthemr_reset()

```


THEMES (g)
==============================================================================

Column 
-----------------------------------------------------------------------

### `ggthemr("chalk")`

```{r}

library(ggthemr)
ggthemr("chalk")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`chalk`)")

ggthemr_reset()

```

### `ggthemr("copper")`

```{r}

library(ggthemr)
ggthemr("copper")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`copper`)")

ggthemr_reset()

```





Column 
-----------------------------------------------------------------------


### `ggthemr("earth")`

```{r}

library(ggthemr)
ggthemr("earth")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`earth`)")

ggthemr_reset()

```


### `ggthemr("fresh")`

```{r}

library(ggthemr)
ggthemr("fresh")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`fresh`)")

ggthemr_reset()

```


Column 
-----------------------------------------------------------------------


### `ggthemr("grape")`

```{r}

library(ggthemr)
ggthemr("grape")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`grape`)")

ggthemr_reset()

```


### `ggthemr("grass")`

```{r}

library(ggthemr)
ggthemr("grass")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`grass`)")

ggthemr_reset()

```


THEMES (h)
==============================================================================

Column 
-----------------------------------------------------------------------

### `ggthemr("greyscale")`

```{r}

library(ggthemr)
ggthemr("greyscale")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`greyscale`)")

ggthemr_reset()

```

### `ggthemr("light")`

```{r}

library(ggthemr)
ggthemr("light")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`light`)")

ggthemr_reset()

```





Column 
-----------------------------------------------------------------------


### `ggthemr("lilac")`

```{r}

library(ggthemr)
ggthemr("lilac")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`lilac`)")

ggthemr_reset()

```


### `ggthemr("pale")`

```{r}

library(ggthemr)
ggthemr("pale")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`pale`)")

ggthemr_reset()

```


Column 
-----------------------------------------------------------------------


### `ggthemr("sea")`

```{r}

library(ggthemr)
ggthemr("sea")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`sea`)")

ggthemr_reset()

```


### `ggthemr("sky")`

```{r}

library(ggthemr)
ggthemr("sky")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`sky`)")

ggthemr_reset()

```


THEMES (i)
==============================================================================

Column 
-----------------------------------------------------------------------

### `ggthemr("solarized")`

```{r}

library(ggthemr)
ggthemr("solarized")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: ggthemr(`solarized`)")

ggthemr_reset()

```

### `theme_lab()` [Trafforddatalab](https://www.trafforddatalab.io/graphics_companion/)

```{r}

source("https://github.com/traffordDataLab/assets/raw/master/theme/ggplot2/theme_lab.R")

ggplot(grafico, aes(x = continent, y = promedio, fill = continent)) +
  geom_col() +
  labs(title = "life expectancy (mean) by continent in 2007",
       subtitle = "theme: theme_lab()") +
  theme_lab()


```



Column 
-----------------------------------------------------------------------


### 

```{r}

```


### 

```{r}



```


Column 
-----------------------------------------------------------------------


### 

```{r}



```


### 

```{r}


```
